---
title: "Solution: s3-hadley-ex.Rmd"
author: "Victor Tuekam"
date: "16 January 2021"
---

1. The function `as.data.frame.data.frame()` implements the `data.frame()` method (for objects of the class `data.frame`) of the generic `as.data.frame`.
   The naming convention for  `s3` methods is `generic.class()`. Here it is difficult to see where the generic part and the class part is, because of so many `.` dots.
   A solution would be a different naming convention that clearly separates the class identifier from the generic. Perhaps `snake_case`.

2.
```{r, eval=FALSE}
set.seed(1014)
# generates 5 random dates after 24. Nov. 2019 up to the 4. Dec. 2020
some_days <- as.Date("2019-11-24") + sample(10, 5)

# calls mean.Date for date objects
# s3_dispatch(mean(some_days))
# => mean.Date
#  * mean.default
mean(some_days)
# [1] "2019-11-30"

# calls mean.default for the storage type of date( which probably calls mean.double)
# typeof(unclass(some_days))
# [1] "double"
# s3_dispatch(mean(unclass(some_days)))
#    mean.double
#    mean.numeric
# => mean.default
mean(unclass(some_days))
# [1] 18230.4
```

3.
```{r, eval=FALSE}
x <- ecdf(rpois(100, 10))
x

# class
class(x)
# [1] "ecdf"     "stepfun"  "function"

# base type
typeof(x)
# [1] "closure"

# attributes
attributes(x)
# $class
# [1] "ecdf"     "stepfun"  "function"
#
# $call
# ecdf(rpois(100, 10))
#
```

The mathematical properties of distribution functions is implemented here using an interpolation function `approxfun`, this can be seen in the source definition of `ecdf`.

4.
```{r}
new_data.frame <- function(data_frame, length, row.names = NULL) {
  # uses a list as base type (str(unclass(mtcars)))
  stopifnot(is.list(data_frame))

  if (is.null(row.names)) {
    row.names <- 1:length
  } else {
    stopifnot(is.character(row.names), length(row.names) == length)
  }

  structure(data_frame,
    row.names = row.names,
    class = "data.frame"
  )
}
```

5.

- Scalar style: `lm()`, `ecdf()`
- Vector style: `factor()`, `table()`, `as.Date()`, `as.POSIXct()`, `ordered()`

6. A constructor of the `lm` class would assign the class $lm$ to objects with the necessary attributes of the `lm` class. `?lm` indicates that an `lm` object is a list containing at least the following components: `coefficients`, `residuals`, `fitted.values`, `rank`, `weights` and many more. Obviously the constructor would check the type of these components.

7. `t.test()` is a generic because it calls `Use.Method("t.test")`.
 The function `t()` is a generic that transposes a matrix. If this function is called on an object of type `test`, the method `t.default()` will be called as there is no method `t.test()` on objects of class `test` (since `t.test()` is a generic).
